From DSL to HPC Component-Based Runtime:\\ A Multi-Stencil DSL Case Study

### 2015-07-29 WOLFHPC15/article/mscac.tex
overview helene 29_07

As illustrated in Figure~\ref{fig:mscac}, the compiler, called MSCAC for \emph{Multi-Stencil Component Assembly Compiler}, is composed of three different phases. The first phase of the compiler is to \emph{parse} the MSL description. Second, the compiler analyzes and transforms the computation part of the description, in other words $\Gamma$. This phase of compilation, called MSC, is responsible for the automatic parallelization of the overall numerical simulation. It transforms $\Gamma$ to a new parallel representation. Finally, the parallelized representation can be dumped to an actual implementation of the parallel structure of the simulation.

@@

The back-end of the compiler is to build a parallel assembly of components, in other words appropriate connections between functionnalities of the numerical simulation. This assembly is illustrated in Figure~\ref{fig:assembly} which is explained in details in Section~\ref{sect:component}. As illustrated in the figure, each component is linked to one or more tuple of the multi-stencil program definition: \emph{DDS} component represents $\mathcal{M}$, $\mathcal{D}_m$; \emph{Data} component represents $\Delta$ and $\mathcal{D}_c$; \emph{Time} component represents $T$, and \emph{Computations} component (which generated by MSC) represents $\Gamma$.

The final back-end component assembly is a ready-to-fill parallel structure where the user only has to actually write computation codes described in the MSL description. To write those computations, interfaces of the choosen implementation have to be used. For example, the back-end evaluated in this paper uses the distributed data structure proposed in SkelGIS library~\cite{CPE:CPE3494}, however a work in progress replace this DDS component by another one using Global Arrays~\cite{Nieplocha:2006:AAP:1125980.1125985} data structures.

>>>>

As illustrated in Figure~\ref{fig:mscac}, the compiler, called MSCAC for \emph{Multi-Stencil Component Assembly Compiler}, is composed of three different phases. The first phase of the compiler is to \emph{parse} the MSL description. Second, the compiler analyzes and transforms the computation part of the description, in other words $\Gamma$, to an intermediate representation. This phase of compilation, called MSC, is responsible for the automatic parallelization of the overall numerical simulation. Finally, the parallel intermediate representation can be dumped to an actual implementation of the parallel structure of the simulation.

@@

The back-end of the compiler is to build a parallel assembly of components, in other words appropriate connections between functionnalities of the numerical simulation. This assembly is illustrated in Figure~\ref{fig:assembly} which is explained in details in Section~\ref{sect:component}. As illustrated in the figure, each component is linked to one or more tuple of the multi-stencil program definition: \emph{DDS} component represents $\mathcal{M}$ and $\mathcal{D}_m$; \emph{Data} component represents $\Delta$ and $\mathcal{D}_c$; \emph{Time} component represents $T$, and \emph{Computations} component (which is generated by MSC) represents $\Gamma$.

The final back-end component assembly is a ready-to-fill parallel structure where the user has to write computation codes described in the MSL description. To write those computations, interfaces of the choosen implementation have to be used. For example, the back-end evaluated in this paper uses the distributed data structure proposed in SkelGIS library~\cite{CPE:CPE3494}, however a work in progress replaces this DDS component by another one using Global Arrays~\cite{Nieplocha:2006:AAP:1125980.1125985} data structure.
